---
title: "FP - DiD: Moser and Voena (2012) [100 Points]"
subtitle: "ECON 474 Econometrics of Policy Evaluation"
author: "FirstName LastName"
output: 
  html_document:
    toc: yes
    toc_float: true
    number_sections: true
    theme: cerulean
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# **[30 Points]** Research Design
********************************************************************************

This section is centered around understanding the research design for this paper.

## **[10 Points]** Research Question
************************************************************

What is the research question of this paper?

*Hint: economists are notorious for not explicitly stating their research question in their papers.*

**Your answer:**



## **[20 Points]** Empirical Design
************************************************************

1. What is the casual technique of this paper, and why is it chosen?

**Your answer:**


2. Name one possible threat to identification.

**Your answer:**


# **[70 Points]** Replication
********************************************************************************

The paper estimates the regression:

$$PatentsByUSInventors_{c,t} = \alpha_t + \alpha_c + \delta(TREAT \times postTWEA)_{c,t} + \gamma X_{c,t} + \epsilon_{c,t}$$

where $t$ is patent subclass and $c$ is patent subclass. 
Since the data are at the patent-level and not the patent subclass-level, your will need to **cluster the standard errors.**

The mapping of the variables in the regression to the data are:

- $c$ - `class_id` (subclass)
- $t$ - `grntyr` (year)
- $PatentsByUSInventors_{c,t}$ - `count_usa`
- $TREAT_c$ - `licensed_subclass`
- $postTWEA_t$ - `grntyr >= 1919` (not in the data set)
- $(TREAT \times postTWEA)_{c,t}$ - `treat`
- $X_{c,t}$ - `count_for` (number of patents by foreign investors)

*Note:* `treat` *does not map perfectly to* `licensed_subclass` $\times$ `(grntyr >= 1919)` *due to the restriction that the subclass has at least one enemy-owned patent.*


**[5 Points]** Load in the data and any necessary packages:

```{r loading please wait}

```


## **[30 Points]** Main Results: Table 2 Columns 1 and 2
************************************************************

Using `treat`, replicate columns 1 and 2 from table 2 in an `etable()`.
Rename all variables appropriately (recall you cannot rename the cluster variable).
Specify the `fitstat` argument appropriately.
Use the `extralines` argument of the `etable()` to:

1. Add any missing elements
2. Add the effect size following the papers methodology
    - *Hint: follow the paper by obtaining the* $\delta$ *coefficients and then divide them by average* `count_usa` *for the __post__ treatment period.*


```{r tab2}

```



## **[35 Points]** Event Study - Figure 4
************************************************************

Figure 4 of the paper is specified in a way that does not transparently show parallel pre-trends (as you will see soon).
We are going to correct it. 

Produce a corrected event study figure that follows what we have done in class with appropriately labelled axes and title with a vertical line for the event date (1919) and a horizontal line at zero.
Your regression will need to control for `count_for`.

**Hints:**

- This time don't use `treat`. Instead use `licensed_class` and `grntyr`. 
- Create a variable `year_factor` that has a base year of 1919
- use `geom_ribbon()` instead of `geom_errorbar()` for a cleaner figure


```{r event study}

```














