---
title: "FP - RDD: Reimers (2019) [100 Points]"
subtitle: "ECON 474 Econometrics of Policy Evaluation"
author: "FirstName LastName"
output: 
  html_document:
    toc: yes
    toc_float: true
    number_sections: true
    theme: cerulean
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# **[30 Points]** Research Design
********************************************************************************

This section is centered around understanding the research design for this paper.

## **[10 Points]** Research Question
************************************************************

What is the research question of this paper?

*Hint: economists are notorious for not explicitly stating their research question in their papers.*

**Your answer:**



## **[20 Points]** Empirical Design
************************************************************

1. What is the casual technique of this paper, and why is it chosen?

**Your answer:**


2. Name one possible threat to identification.

**Your answer:**


# **[70 Points]** Replication
********************************************************************************

The paper estimates the regression:

$$y_j = \delta 1\{IP =1\} + k(year_j) + X_j \beta + \epsilon_j$$

where $j$ is the specific book title (e.g. Gone with the Wind).

The mapping of the variables in the regression to the data are:

- $y_j$
    - `ntitle` - number of in-print editions per title
    - `ntitleformat` - number of in-print editions per title for each format (e.g. hardcover, paperback, e-book)
- $1\{IP =1\}$ - `post1923` (publication year $\geq$ 1923)
- $k(year_j)$ - a third degree polynomial of `year`
- $X_j$
    - `plr` - British Public Library Demand (checkouts)
    - `prize_author` - Author is a Pulitzer Prize winner
    - `canon_title` - Book listed in Harold  Bloom's Western Canon: The Books and School of the Ages
    - `canon_author` - Author listed in Harold  Bloom's Western Canon: The Books and School of the Ages

Additionally, there is a variable `format` that lists the formats in which the book is published.


**[5 Points]** Load in the data and any necessary packages:

```{r loading please wait}

```

*Note: if you are still confused what this paper is analyzing, go to Amazon and search for the Wealth of Nations. There are __many__ different versions of the same book. This is not the case for a book that has been published recently.*

## **[30 Points]** Main Results: Table 2
************************************************************

The regressions in table 2 only consider `year`s that are $\geq$ -8 years before the cutoff and $\leq$ 7 years after the cutoff.
All regressions cluster on the `year` of publication variable.
The column specific details are:

1. outcome `ntitle` on the additional subset of `"Hardcover"` `format`s
2. outcome `ntitleformat` on the additional subset of `"Hardcover"` `format`s
3. outcome `ntitleformat` on the additional subset of `"Paperback"` `format`s
4. outcome `ntitleformat` on the additional subset of `"E-book"` `format`s

Replicate table 2 in an `etable()`.
Rename all variables appropriately (recall you cannot rename the cluster variable).
Specify the `fitstat` argument appropriately.
Use the `extralines` argument of the `etable()` to:

1. Add any missing elements
2. Add the effect size following the papers methodology
    - *Hint: Obtain the* $delta$s *and then divide them by the __pre-cutoff__ averages of the outcome variables for the __subsample that matches the regressions__.*
    
*Note: the coefficients on the polynomial and the intercept will be different than the paper but the rest will be the same.*

```{r tab2}

```



## **[35 Points]** RDD Plot - Figure 1
************************************************************


Replicate Figure 1 with appropriately labelled axes and title, which uses a third-order polynomial on each side of the cutoff on the outcome `ntitle`. 
Do not remove the standard error from the fitted line.

*Hint: create another data frame that is aggregated at the annual level, and adjust the* `year` *variable.*

*Note: the figure will not be identical but will be close to the one in the paper.*

```{r RDD figure}

```











